\section{Introduction}
\label{sec:intro}

%From the emergence of generative networks like generative adversarial networks (GANs) to large generative models like diffusion models and large language models (LLMs), generative AI has shown its increasing capability of generating high-quality, creative text and media.
%This progress has facilitated the production and distribution of \textit{AI-generated content}, raising critical challenges about online trust and safety. To date, stakeholders---including regulators, AI service providers, online platforms, and researchers---have been actively addressing those challenges, which we refer to as \textit{governance of AI-generated content} in online spaces. 

The rapid development of large generative models and generative AI products has led to a sudden surge of \textit{AI-generated content} in online spaces. This surge has fundamentally altered the scale, visibility, and role of generative AI in online content consumption~\cite{liang2025widespread,matatov2024examining,wei2024understanding,sun2025we,hua2024generative,guo2025exploring}, raising challenges for the \textit{governance of AI-generated content} to maintain trust and safety. While the governance of AI-generated content can be traced back to the adoption of early AI techniques capable of producing realistic media (i.e., the governance of \textit{deepfakes} and \textit{synthetic media})~\cite{westerlund2019emergence}, the recent landscape evolution of large models marks a departure from the conditions under which existing governance approaches initially took shape. In this paper, we revisit the development of AI-generated content governance and explore future paradigms that can better respond to the impacts of the recent large-scale proliferation of AI-generated content online.

Stakeholders have already devoted substantial efforts to addressing the risks posed by AI-generated content. Yet, current governance actions remain largely confined to addressing explicit harms and follow an incident-based logic: moderating AI-generated content that maps into established online harm categories, under a relatively clear threat model of attacker, victim, harm, and consequence. For example, in general-purpose generative AI products, the primary focus of governance is on preventing harmful output and service abuse, such as prohibiting the generation of disturbing, privacy-violating, and explicit content~\cite{gao2025cannot,riccio2024exploring,klyman2024acceptable}. In online platforms like social media, governance actions primarily focus on enforcing existing community guidelines or improving content authenticity through labeling AI-generated content. Few platforms have addressed unique challenges in AI-generated content like ownership and monetization via new rules~\cite{gao2026governance}, and often these topics are addressed through user-driven, bottom-up efforts~\cite{lloyd2025there,lloyd2025ai}. These new policies are also largely one-cut restrictive~\cite{lloyd2025ai, gao2026governance}, such as completely banning the monetization of AI-generated content~\cite{gao2026governance}.

Here, we argue that the current incident-based governance targeting explicit harms, while essential, may be insufficient to address the increasingly routine and large-scale use of generative AI in online spaces. As AI-generated content becomes pervasive, many consequential effects are diffuse, gradual, and difficult to delineate, through which negative impacts can accumulate and eventually compromise trust and safety. For example, high-volume, low-effort AI-generated posts (``AI slop'') can erode users’ perceived information value and credibility at the community level, even when individual items are not inherently harmful~\cite{Gross2025AISlopAP, mahdawi2025slop, hoffman2024first}. The widespread use of generative AI complicates ownership, authorship, and originality of creative works~\cite{10.1145/3706598.3713522,kyi2025governance}. In online spaces, such controversies pose challenges for allocating credit and accountability in algorithmic promotion and monetization~\cite{cosen2024new}. As AI-mediated communication---where communicators adopt AI to modify, augment, or generate messages to accomplish communication goals~\cite{hancock2020ai}---becomes increasingly common, the boundaries between AI-generated and human-made content are likely to be further blurred, eventually reforming perceptions of content authenticity and value online~\cite{Gross2025AISlopAP, eissa2025influence}. These emerging challenges, though often not causing immediate damage, could eventually compromise user experiences, creator rights, and community values if not well-addressed. And they are either not covered by the current governance targeting explicit harms, or cannot be addressed perfectly through an incident-based logic as currently implemented. %\mc{this next sentence seems very clear about the goal of the paper} 

In this position paper, we suggest that the future governance of AI-generated content should extend its scope from incident-based, explicit harm mitigation to address AI-generated content's broad socio-technical and epistemic impacts on the online information ecosystem. We begin by clarifying the definition of AI-generated content and its governance in this paper. Then, we synthesize the development of current governance of AI-generated content from regulations, policymaking, technical developments, and research. After that, we discuss why governance of AI-generated content should extend beyond an incident-based framework focused on mitigating explicit harms to also address emergent challenges arising from the surge of AI-generated content and everyday generative AI uses. We finally outline recommendations for online platforms, AI developers, regulators, and researchers to improve the future governance of AI-generated content in online spaces.

The main contributions of our paper are to enhance AI governance and trust and safety efforts in the research community and industry, by providing an overview of current AI-generated content governance and why they fall short of addressing holistic socio-technical shifts that it is making on the online information ecosystem. Our synthesis and argument help with direction-setting for both academia and industry. In addition, we contribute concrete recommendations for researchers, policymakers, and industry practitioners on how best to get ahead of this shift as generative AI continues to evolve.
%\mc{you might need something somewhere that explains that you use the latest research to substantiate your claims so folks know this is based on literature, from the citations in the text throughout its not as clear what is from current literature. need something that says we examine current literature in SOUPS/HCI etc to back up these argeuments including studies we have conducted - make the paper feel more grounded, should look at how others have addressed this e.g. check the Shaowen Bardzell on feminism in HCI or Eli Blevis on sustainabilty in HCI papers} \lan{maybe add this to the paragraph above?---already added a short review scope clarification at the beginning of section 3, but wondering if we should say more in intro}
 

